A unified model for parsing and sentence understanding

### 2016-03-12 writing/hard_stack_paper/batching_fig.tex
Post-coffee paper progress.

\begin{figure}[t]
\begin{subfigure}[t]{0.9\columnwidth}
\begin{center}
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]
    \tikzstyle{alt}=[fill=orange!40]    
    \pgfsetarrowsend{latex}
    \tikzset{edge from parent/.append style={<-, line width=1pt}}

@@

    \Tree [.\node[nonleaf,alt](2thekittenate){the old cat ate}; [.\node[nonleaf,alt](2thekitten){the old cat}; \node[word,alt](2the){the}; [.\node[nonleaf,alt](2bigkitten){old cat}; \node[word,alt](2kitten){old}; \node[word,alt](2kitten){cat}; ] ] \node[word,alt](2ate){ate}; ]

@@

    \begin{scope}[shift={(0.9in,-0.8in)}, frontier/.style={distance from root=60pt}]

    \Tree [.\node[nonleaf](1thecatsatdown){the cat sat down}; [.\node[nonleaf](1thecat){the cat}; \node[word](1the){the}; \node[word](1cat){cat}; ] [.\node[nonleaf](1satdown){sat down}; \node[word](1sat){sat}; \node[word](1down){down}; ] ]

@@

\begin{subfigure}[t]{0.9\columnwidth}
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black] 
    \tikzstyle{alt}=[fill=orange!40]
    \pgfsetarrowsend{latex}
    \tikzstyle{fwd} = [draw=black, line width=1pt]

    \def\dx{26pt}
    \def\dy{11pt}
    \def\sy{7*\dy}
    \def\oxb{5.5*\dx}
    \def\by{1*\dy}
    \def\ox{0*\oxb}

    \node[word,alt]  (n1) at (\ox+-3*\dx,\by+3*\dy) {~~~~~};
    \node[word,alt]  (n2) at (\ox+-1*\dx,\by+3*\dy) {~~~~~};
    \node[word,alt]  (n3) at (\ox+1*\dx,\by+3*\dy) {~~~~~};
    \node[word,alt]  (n4) at (\ox+3*\dx,\by+3*\dy) {~~~~~};

   \draw [fwd] (n1) -- (n2);
   \draw [fwd] (n2) -- (n3);
   \draw [fwd] (n3) -- (n4);

    \node[word]  (n1) at (\ox+-3*\dx,\by+3*\dy) {~~~~~};
    \node[word]  (n2) at (\ox+-1*\dx,\by+3*\dy) {~~~~~};
    \node[word]  (n3) at (\ox+1*\dx,\by+3*\dy) {~~~~~};
    \node[word]  (n4) at (\ox+3*\dx,\by+3*\dy) {~~~~~};

   \draw [fwd] (n1) -- (n2);
   \draw [fwd] (n2) -- (n3);
   \draw [fwd] (n3) -- (n4);

\caption{\label{fig:batching:good}A conventional sequence-based RNN, instantiated for two sentences.}
\end{subfigure}
\caption{An illustration of two standard designs for sentence encoders. Note that the TreeRNN, unlike the sequence-based RNN, requires a substantially different connection structure for each sentence.}
\end{figure}

>>>>

\begin{figure}[t]

\begin{subfigure}[t]{\columnwidth}
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black] 
    \tikzstyle{alt}=[fill=orange!40]
    \pgfsetarrowsend{latex}
    \tikzstyle{fwd} = [draw=black, line width=1pt]

    \def\dx{23pt}
    \def\dy{11pt}
    \def\sy{7*\dy}
    \def\oxb{5.5*\dx}
    \def\by{1*\dy}
    \def\ox{0*\oxb}

    \node[word,alt]  (n1) at (\ox+-3*\dx,\by+3*\dy) {~~~~~};
    \node[word,alt]  (n2) at (\ox+-1*\dx,\by+3*\dy) {~~~~~};
    \node[word,alt]  (n3) at (\ox+1*\dx,\by+3*\dy) {~~~~~};
    \node[word,alt]  (n4) at (\ox+3*\dx,\by+3*\dy) {~~~~~};
    \node[]  (n5) at (\ox+4.5*\dx,\by+3*\dy) {...};

   \draw [fwd] (n1) -- (n2);
   \draw [fwd] (n2) -- (n3);
   \draw [fwd] (n3) -- (n4);
   \draw [fwd] (n4) -- (n5);

    \node[word]  (n1) at (\ox+-3*\dx,\by+3*\dy) {~~~~~};
    \node[word]  (n2) at (\ox+-1*\dx,\by+3*\dy) {~~~~~};
    \node[word]  (n3) at (\ox+1*\dx,\by+3*\dy) {~~~~~};
    \node[word]  (n4) at (\ox+3*\dx,\by+3*\dy) {~~~~~};
    \node[]  (n5) at (\ox+4.5*\dx,\by+3*\dy) {...};

   \draw [fwd] (n1) -- (n2);
   \draw [fwd] (n2) -- (n3);
   \draw [fwd] (n3) -- (n4);
   \draw [fwd] (n4) -- (n5);

\caption{\label{fig:batching:good}A conventional sequence-based RNN, instantiated for two sentences.}
\end{subfigure}

\begin{subfigure}[t]{\columnwidth}
\begin{center}
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]
    \tikzstyle{alt}=[fill=orange!40]    
    \pgfsetarrowsend{latex}
    \tikzset{edge from parent/.append style={<-, line width=1pt}}

@@

    \Tree [.\node[](root){...}; [.\node[nonleaf,alt](2thekittenate){the old cat ate}; [.\node[nonleaf,alt](2thekitten){the old cat}; \node[word,alt](2the){the}; [.\node[nonleaf,alt](2bigkitten){old cat}; \node[word,alt](2kitten){old}; \node[word,alt](2kitten){cat}; ] ] \node[word,alt](2ate){ate}; ] ]

@@

    \begin{scope}[shift={(0.9in,-0.8in)}]

    \Tree [.\node[](root){...}; [.\node[nonleaf](1thecatsatdown){the cat sat down}; [.\node[nonleaf](1thecat){the cat}; \node[word](1the){the}; \node[word](1cat){cat}; ] [.\node[nonleaf](1satdown){sat down}; \node[word](1sat){sat}; \node[word](1down){down}; ] ] ]

@@

\caption{An illustration of two standard designs for sentence encoders. Note that the TreeRNN, unlike the sequence-based RNN, requires a substantially different connection structure for each sentence.}
\end{figure}

### 2016-03-12 writing/hard_stack_paper/paper.tex
Post-coffee paper progress.

%    \author{
%    Samuel R.\ Bowman$^{1,2,5,}$\thanks{The first two authors contributed equally.} \\
%    \texttt{\small sbowman@stanford.edu} \\
%    \And
%    Jon Gauthier$^{2,3,5,*}$ \\
%    \texttt{\small jgauthie@stanford.edu} \\
%    \And
%    Abhinav Rastogi$^{4,5}$ \\
%    \texttt{\small arastogi@stanford.edu} \\
%    \AND
%    Raghav Gupta$^{6}$ \\
%    \texttt{\small rgupta93@stanford.edu} \\
%    \And
%    Christopher D.\ Manning$^{1,2,5,6}$\\
%    \texttt{\small manning@stanford.edu}\\
%    \And
%    Christopher Potts$^{1}$\\
%    \texttt{\small cgpotts@stanford.edu}
%    \AND\\[-3ex]
%    {$^{1}$Stanford Linguistics\quad
%    $^{2}$Stanford NLP Group\quad
%    $^{3}$Stanford Symbolic Systems}\\
%    {$^{4}$Stanford Electrical Engineering\quad
%    $^{5}$Stanford AI Lab\quad
%    $^{6}$Stanford Computer Science}
%    }

@@

\begin{itemize}

\item Brief history of TreeRNNs
\begin{itemize}
\item Lx theory suggests should be better than comparable sequence models via compositionality \cite{Partee84,Janssen97}.
\item In practice, results mixed but positive. \citealt{tai2015improved} shows dramatic gains on sentiment analysis using tree-structured models over sequence models. \citealt{li2015tree} shows mixed results. Both of these evaluations are limited to small datasets with only hundreds or thousands of training examples.
\item Larger evaluations have been impossible due to issues of computational efficiency. One aim of this paper is to mitigate these issues to make larger-scale experiments possible.
\item Note, though, that while tree structure can be seen as a bias, simply adding more data within reason may not be enough to get a sequence model to learn without that bias \citealt{bowman2015trees}.
\end{itemize}

\item Speed issues
\begin{itemize}
\item Efficient batched computation is a crucial enabling technology in allowing NNs to be used on large datasets. Since NNs require large datasets to be able to model complex problems like language understanding, this is crucial in NLP.
\item Tree structured neural networks can't be batched. As the schematic in Figure~\ref{fig:batching:bad} indicates, different sentences are assigned different trees, and there is no straightforward way of aligning these trees to synchronize computation in the conventional style of implementation.
\item In addition, the requirement of an external parser complicated pipeline-building, and slows down inference. This is not necessarily a practical limitation, since modern parsers can assign reasonably high quality parses in so little time as to not dramatically impact the performance characteristics of our model \todo{[SB,JG,CM] How fast are fast constit parsers?}.

\item Our model
\begin{itemize}
\item In this paper, we present the Parser--Interpreter NN (PINN)

\item Attention issues
\begin{itemize}
\item The technique of soft attention has proven to be exceptionally effective as a way of training neural network models for tasks like translation \cite{bahdanau2014neural,luong-pham-manning:2015:EMNLP} and natural language inference \cite{rocktaschel2015reasoning}.
\item This paper proposes two complementary extensions of the idea of attention to tree-structured models:
\begin{itemize}
\item Constituent-by-constituent attention, in which each node in the tree of one sentence is given a soft alignment to some node or nodes in a second sentence.
\item The mTreeLSTM, which uses a third tree structured model to accumulate information about the alignment between two sentences into a single feature vector. This builds on the notion of a matching LSTM or mLSTM from \citealt{DBLP:journals/corr/WangJ15b}.
\end{itemize}
\end{itemize}

\item Outline of the paper
\begin{itemize}
\item Propose a model
\item Show how the model can be used for NLI
\item Show how attention can be used on the NLI model
\item Experiments and discussion
\end{itemize}

@@

\subsection{The model}

The PINN, which is shown in Figure~\ref{fig:model:0}, takes the form of a transition-based parser, but it is designed to produce sentence representations given parse structures, rather than producing parse structures as its output, leading to the following differences: \todo{[SB] Swap in Model 1 fig.}
\begin{itemize}
\item The model takes a sequence of transitions (\shift s or \reduce s) as input, rather than incorporating a decision function which chooses which transition to perform at each step.
\item The intermediate representations in the parser, including the representations of the tree structures on the stack, are vectors of a fixed length.
\item The \reduce~operation, which combines two trees or tree nodes on the stack into a single larger tree, is represented using a parametric neural network layer function (in particular, a TreeLSTM layer, after \citealt{tai2015improved}).
\item The intermediate states of the stack and buffer during parsing are stored during training. This makes it possible to learn the parameters of the composition function and the input word representations that are fed into the buffer using backpropagation on an objective function that depends on the final sentence representation that emerges at the head of the stack.
\item A novel tracking LSTM component is added to improve the model's ability to efficiently track the context in which each step is being performed.
\item A variant, PINN-GT uses ground truth parse information at training and test time, and omits the prediction layer.
\end{itemize}

\input{../model0_fig.tex}

@@

\paragraph{The representations in the stack}

@@

Our composition function is based closely on the TreeLSTM of \citealt{tai2015improved}. The TreeLSTM generalizes the LSTM neural network layer \cite{hochreiter1997long} to tree- rather than sequence-based inputs, and it shares with that older design the idea of representing intermediate states in a computation using a two-part vector representation containing an $\vec{h}$ vector and a $\vec{c}$ vector, where the latter is meant to serve as a slower-changing long-term memory.

The precise formulation that we use is as follows.

\begin{gather}
\colvec{4}
    {\vec{i}}
    {\vec{f}_l}
    {\vec{f}_r}
    {\vec{o}}
= \sigma(
W_{\text{iffo}}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
)
\\
\vec{g}
= \tanh(
W_{g}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
)
\\
\vec{c} = \vec{f}_l * \vec{c}_s^2 + \vec{f}_r * \vec{c}_s^1 + \vec{i} * \vec{g}  
\\
\vec{h} = \vec{o} * \vec{c}
\end{gather}

The results of this function are the pair $(\vec{h}, \vec{c})$, which are placed back on the stack. The two input tree nodes popped off the stack are represented as the pairs $(\vec{h}^1_s, \vec{c}^1_s)$ and $(\vec{h}^2_s, \vec{c}^2_s)$. In addition, $\vec{e}$ is an optional input argument which is either the empty vector $[]$ or a vector from an external source like the tracking LSTM (see below). $*$ denotes the elementwise product. Each vector-valued variable listed here is of dimension $D$, except $\vec{e}$, which is of dimensions $D_t$, which can be chosen independently.

@@

\subsection{Tracking left context with an auxiliary LSTM}

@@

\todo{[SB] Fill in math, Explain.}

@@

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Params.    & Trans. acc.  &   Train  &   Test \\
\midrule
\multicolumn{4}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                & --                    &   99.7   &   78.2      \\
\midrule
\multicolumn{4}{c}{Previous NN results without attention}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               & --               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & --              &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m                & --             &   83.4   &   82.1       \\
\midrule
\multicolumn{4}{c}{Previous NN results with attention}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               & --              &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               & --             &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long}
                        & 1.4m               & --                &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule
\result{300d LSTM RNN      } & ?             & --                &   ?      &   81?       \\
\result{300d PINN-GT w/o tracking}   
                        & ?                  & --                &   ?      &   81?       \\
\result{300d PINN-GT }
                        & ?                  & --                &   ?      &   83?       \\
\result{300d PINN }
                        & ?                  & ??                  &   ?      &   83?       \\                        
\result{300d PINN-GT, sequence-based attn.   }     
                        & ?                  & --                &   ?      &   85+?       \\
\result{300d PINN-GT, tree-based attn. }           
                        & ?                  & --                &   ?      &   \textbf{?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for models where they are trained). Trans. acc. is the model's accuracy in predicting parsing transitions. Train and test are SNLI classification accuracy. \result{[JG]Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}

@@

>>>>

     \author{}
%    \author{
%    Samuel R.\ Bowman$^{1,2,5,}$\thanks{The first two authors contributed equally.} \\
%    \texttt{\small sbowman@stanford.edu} \\
%    \And
%    Jon Gauthier$^{2,3,5,*}$ \\
%    \texttt{\small jgauthie@stanford.edu} \\
%    \And
%    Abhinav Rastogi$^{4,5}$ \\
%    \texttt{\small arastogi@stanford.edu} \\
%    \AND
%    Raghav Gupta$^{6}$ \\
%    \texttt{\small rgupta93@stanford.edu} \\
%    \And
%    Christopher D.\ Manning$^{1,2,5,6}$\\
%    \texttt{\small manning@stanford.edu}\\
%    \And
%    Christopher Potts$^{1}$\\
%    \texttt{\small cgpotts@stanford.edu}
%    \AND\\[-3ex]
%    {$^{1}$Stanford Linguistics\quad
%    $^{2}$Stanford NLP Group\quad
%    $^{3}$Stanford Symbolic Systems}\\
%    {$^{4}$Stanford Electrical Engineering\quad
%    $^{5}$Stanford AI Lab\quad
%    $^{6}$Stanford Computer Science}
%    }

@@

A wide range of current state-of-the-art models in NLP are built around neural network components that build vector representations of sentence meaning \cite{socher2011semi,sutskever2014sequence} \todo{[SB] Cite Oriol's conversation paper.}. This component, the sentence encoder, is generally formulated as a learned parametric function from word vectors to sentence vectors, and this function can take a range of different forms. Common sentence encoders include sequence-based recurrent neural network models (RNNs) with Long Short-Term Memory (\citealt{hochreiter1997long}, see Figure~\ref{fig:batching:good}), which accumulate information over the sentence sequentially, convolutional neural networks over words or characters \cite{kalchbrenner2014convolutional} \todo{Cite LeCun CharConvNet}, which pool information over short localsequences of words, and tree-structured recursive neural networks (TreeRNNs \citealt{goller1996learning,socher2011semi}, see Figure~\ref{fig:batching:bad}), which propagate information up a binary tree structure over the words. Of these, there are tidy theoretical arguments suggesting that the TreeRNN is the principled choice: meaning in natural language sentences is widely believed to be constructed incrementally according to a tree-structure \cite{Partee84,Janssen97}, and so a model which instantiates that tree structure should have a maximally easy time recovering the process by which meaning is constructed.

In practice, TreeRNNs have shown promise, but they have largely been overlooked in favor of sequence-based RNNs for practical reasons. Batched computation--performing synchronized computation across many examples at once--is a crucial enabling technology in allowing neural networks to be trained efficiently on large datasets \question{What, if anything, can we cite here?}. Batching yields order-of-magnitude improvements in standard CPU implementation, and substantial additional gains on GPUs. TreeRNNs build the parse structure of each sentence they process into the structure of the network itself, forcing the model to perform a different sequence of computations for each sentence, and thereby requiring that each sentence be processed one-by-one, making batched computation impossible. One aim of this paper is to make these large-scale evaluations possible. Beyond even this large handicap, TreeRNNs can only operate on sentences that have already been processed by a syntactic parser, which slows and complicates the implementation of these models for most applications.

In spite of the unwieldiness of current standard TreeRNNs, there is still value in the idea of using syntactic parse trees to guide the construction of meaning in neural network models. Tree-structured models have shown substantial performance gains on some smaller-scale NLP tasks \cite{tai2015improved,li2015tree}, and their theoretical foundations are strong. Tree-structured compositionality is a property of natural language, and simpler sequence-based RNNs have a difficult time exploiting this property---while sequence-based models should, theoretically, be able to learn to simulate tree-structured composition, this behavior does not emerge in practice on reasonably-sized tasks \cite{bowman2015trees}.

In this paper, we introduce the Parser--Interpreter Neural Network, or PINN. The PINN is a model which reimplements tree-structured composition within an alternative design that incorporates a neural network parser. This design improves upon the previous TreeRNN approach to compositionality in three ways:
\begin{itemize}
\item At test time, it can simultaneously parse and interpret unparsed sentences, removing the dependence on an external parser.
\item It supports batched computation for both parsed and unparsed sentences, supporting dramatic speedups over standard TreeRNNs.
\item It supports a novel tree-sequence hybrid mechanism for handling local context in sentence interpretation that yields substantial gains in accuracy over either pure sequence-based models or pure tree-based models.
\end{itemize}

\todo{[SB] Introduce attention here if appropriate.}

\textcolor{gray}{
\begin{itemize}
\item The technique of soft attention has proven to be exceptionally effective as a way of training neural network models for tasks like translation \cite{bahdanau2014neural,luong-pham-manning:2015:EMNLP} and natural language inference \cite{rocktaschel2015reasoning}.
\item This paper proposes two complementary extensions of the idea of attention to tree-structured models:
\begin{itemize}
\item Constituent-by-constituent attention, in which each node in the tree of one sentence is given a soft alignment to some node or nodes in a second sentence.
\item The mTreeLSTM, which uses a third tree structured model to accumulate information about the alignment between two sentences into a single feature vector. This builds on the notion of a matching LSTM or mLSTM from \citealt{DBLP:journals/corr/WangJ15b}.
\end{itemize}
\end{itemize}
}

The paper is structured as follows: We first introduce the PINN, then demonstrate its application to the task of natural language inference. We then discuss applications of neural attention to the PINN. Finally, we present experimental results and discussion.

\input{../model1_fig.tex}

@@

\subsection{Composition and representation}

The PINN, which is shown in Figure~\ref{fig:model:1d}, takes the form of a transition-based parser, but it is designed to produce sentence representations given parse structures, rather than producing parse structures as its output, leading to the following differences:
\begin{itemize}
\item The intermediate representations in the parser, including the representations of the tree structures on the stack, are vectors of a fixed length.
\item The \reduce~operation, which combines two trees or tree nodes on the stack into a single larger tree, is represented using a parametric neural network layer function (in particular, a TreeLSTM layer, after \citealt{tai2015improved}).
\item The intermediate states of the stack and buffer during parsing are stored during the processing of each sentence at training time. This makes it possible to learn the parameters of the composition function and the input word representations that are fed into the buffer using backpropagation on an objective function that depends on the final sentence representation that emerges at the head of the stack.
\item A novel tracking LSTM component is added to improve the model's ability to efficiently track the context in which each step is being performed.
\item The model can construct sentence representations on sentences which have already been parsed by an external parser. In this setting, which we call PINN-Ext, the model takes a sequence of transitions (\shift s or \reduce s) as an additional input.

This subsection describes the core functions and representations of the PINN.

@@

\paragraph{The stack and buffer}

@@

Our composition function is based on the TreeLSTM of \citealt{tai2015improved}. The TreeLSTM generalizes the LSTM neural network layer \cite{hochreiter1997long} to tree- rather than sequence-based inputs, and it shares with that older design the idea of representing intermediate states in a computation using a two-part vector representation containing an $\vec{h}$ vector and a $\vec{c}$ vector, where the latter is meant to serve as a slower-changing long-term memory.  It is formulated as:

\begin{gather}
\colvec{4}
    {\vec{i}}
    {\vec{f}_l}
    {\vec{f}_r}
    {\vec{o}}
= \sigma(
W_{\text{iffo}}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
)
\\
\vec{g}
= \tanh(
W_{g}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
)
\\
\vec{c} = \vec{f}_l * \vec{c}_s^{\,2} + \vec{f}_r * \vec{c}_s^{\,1} + \vec{i} * \vec{g}  
\\
\vec{h} = \vec{o} * \vec{c}
\end{gather}

The results of this function are the pair $(\vec{h}, \vec{c})$, which are placed back on the stack. The two input tree nodes popped off the stack are represented as the pairs $(\vec{h}^1_s, \vec{c}^{\,1}_s)$ and $(\vec{h}^2_s, \vec{c}^{\,2}_s)$. In addition, $\vec{e}$ is an optional input argument which is either the empty vector $[]$ or a vector from an external source like the tracking LSTM (see below). $*$ denotes the elementwise product. Each vector-valued variable listed here is of dimension $D$, except $\vec{e}$, which is of dimensions $D_t$, which can be chosen independently.

@@

\subsection{Tracking left context with an auxiliary LSTM} \todo{[SB] Recheck.}

@@

The model described so far is the PINN-Ext model, which uses sequences of \shift~and \reduce~operations from an external parser. To build the fully independent PINN model, we simply add a single-layer neural network classifier that chooses which operation to perform at each step using the state of the tracking LSTM:

\begin{equation}

$\vec{p}_{trans}$ = \text{softmax}(M_{trans}\vec{h}_{track})

\end{equation}

\todo{[SB] Objective function, soft v. hard max.}

@@

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Params.    & Trans. acc.  &   Train  &   Test \\
\midrule
\multicolumn{4}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                & --                    &   99.7   &   78.2      \\
\midrule
\multicolumn{4}{c}{Previous NN results without attention}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               & --               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & --              &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m                & --             &   83.4   &   82.1       \\
\midrule
\multicolumn{4}{c}{Previous NN results with attention}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               & --              &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               & --             &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long}
                        & 1.4m               & --                &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule
\result{300d LSTM RNN      } & ?             & --                &   ?      &   81?       \\
\result{300d PINN-Ext w/o tracking}   
                        & ?                  & --                &   ?      &   81?       \\
\result{300d PINN-Ext }
                        & ?                  & --                &   ?      &   83?       \\
\result{300d PINN }
                        & ?                  & ??                  &   ?      &   83?       \\                        
\result{300d PINN-Ext, sequence-based attn.   }     
                        & ?                  & --                &   ?      &   85+?       \\
\result{300d PINN-Ext, tree-based attn. }           
                        & ?                  & --                &   ?      &   \textbf{?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for models where they are trained). Trans. acc. is the model's accuracy in predicting parsing transitions. Train and test are SNLI classification accuracy. \result{[JG]Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}

@@

\todo{Comment on how long top-quality stand-alone greedy parsers take, for comparison.}
